An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-10 draft.tex
reflow
Fix error bibliography
Some rephrasing

\begin{abstract} 
Multi-population based methods have been used extensively in
recent years to improve the performance of nature-inspired optimization
algorithms, these methods are parallel and asynchronous by nature; researchers
take advantage of this to scale algorithms with distributed, multi-threaded,
parallel and cloud-based implementations. However, the design of distributed
versions of multi-population algorithms for their execution in cloud
infrastructures is not a trivial task. Designers need to adapt the algorithms to
leverage the benefits of scalability, elasticity, fault-tolerance,
reproducibility, and cost-effectiveness of reactive cloud-based systems. In this
work, we present the design and implementation of a reactive container-based
application for the execution of multi-population algorithms. Researchers can
use the application to execute multiple experiments, both locally or in a cloud
environment and deploy experiments by specifying the infrastructure as part of
an experiment definition so that it is much easier to reproduce results. We
evaluated the performance of the platform and the benefits of a multi-population
approach by using an ensemble of Genetic Algorithms (GAs) and Particle Swarm
Optimization (PSO) in a benchmark for the optimization of continuous functions.
Experiments show that the framework allows the ensemble to outperform
single-algorithm versions. The framework we provide also has fewer parameters to
tune since subpopulation parameters are selected randomly. The architecture and
the implemented platform is an excellent alternative for locally or a
cloud-based deployment. 
\end{abstract}

@@

\bibliographystyle{elsarticle-num}
\bibliography{multipopulation, serverless}

>>>>

\begin{abstract} 
Multi-population based methods have been used extensively in
recent years to improve the performance of nature-inspired optimization
algorithms, these methods are parallel and asynchronous by nature and researchers
leverage this to scale algorithms % scale algorithms or implementations? - JJ
with distributed, multi-threaded,
parallel and cloud-based implementations. However, the design  of cloud-native,  distributed, multi-population algorithms is not a trivial task. Designers need to adapt the algorithms, while keeping its nature, to
leverage the scalability, elasticity, fault-tolerance,
reproducibility, and cost-effectiveness of reactive cloud-based systems. % reactive is mentioned here for the first time. Possibly you should just refer to "cloud-native" and then specify that it implies asynchrony, reactivity, and so on - JJ
In this
work, we present the design and implementation of a reactive container-based
application for the execution of multi-population algorithms. Researchers can
use the application to execute multiple experiments, both locally or in a cloud
environment and deploy experiments by specifying the infrastructure as part of
an experiment definition so that results are easily reproducible. We
evaluated the performance of the platform and the benefits of a multi-population
approach by using an ensemble of Genetic Algorithms (GAs) and Particle Swarm
Optimization (PSO) in a benchmark for the optimization of continuous functions.
Experiments show that the framework allows the ensemble to outperform
single-algorithm versions. The framework we provide also has fewer parameters to
tune since subpopulation parameters are selected randomly. The architecture and
the implemented platform is an excellent alternative for locally or a
cloud-based deployment.
\end{abstract}

@@

\bibliographystyle{elsarticle-num}
\bibliography{multipopulation,serverless}
